Microxanox - an R package to simulate ...

### 2022-03-22 inst/manuscript/manuscript_microxanox.Rmd
Next step in manuscript

---
title: "Microxanox - an R package to simulate ..."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
bibliography: manuscript_bibliography.bib
date: "`r Sys.time()`"

@@

# qarto output settings
format:
  html:
    self-contained: true
    toc: true
    toc-depth: 3
    link-external-icon: true
    title-block-style: default

# filters:
#   - type: json
#     path: criticpandoc.py

# Citation settings    
nocite: '@Bush2017'
linkcolor: blue
link-citations: yes

csl: methods-in-ecology-and-evolution.csl
---

@@

{>> Biological justification and background - one paragraph <<}

@@

{>> Add a more detailed description of the model and the additions <<}

@@

1. Standard R help for each function (`?COMMAND` in R)
2. Two vignettes acompanying the package, also available under RUniverse [Vignette 1](@LINK_NEEDED) and [Vignette 2](@LINK_NEEDED)
3. This paper as a third vignette, also available under RUniverse [Vignette 3](@LINK_NEEDED)

@@

{>>More details from the paper.<<}

>>>>

---
title: "Microxanox - an R package to simulate ..."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
bibliography: manuscript_bibliography.bib

date: last-modified 
date-format: "DD MMM YYYY, HH:mm"

@@

# qarto output settings
format:
  html:
    self-contained: true
    toc: true
    toc-depth: 3
    link-external-icon: true
    title-block-style: default
  pdf:
    toc: true
    toc-depth: 3
    lof: true
    include-in-header:
      - headers.tex

# Citation settings    
nocite: '@Bush2017'
linkcolor: blue
link-citations: yes
csl: methods-in-ecology-and-evolution.csl
---

@@

{>>Biological justification and background - one paragraph<<}
{>>Rewrite the abstract for this<<}

> Abstract Romana of paper: The role of functional diversity in ecosystem regime shifts

> Biodiversity can increase the resilience of ecosystems facing environmental change. However, we have limited understanding if this holds true for ecosystems that respond to gradual environmental change with abrupt regime shifts. Here we investigated if functional diversity influences the resilience of ecosystems that abruptly transition between alternative ecosystem states. As a case study, we used a mathematical model developed by Bush et al. (2017) which describes anoxic-oxic regime shifts of aquatic ecosystems mediated by cyanobacteria, sulfate-reducing bacteria, and phototrophic sulfur bacteria. We extended this model so as to include functional diversity in one, two, or all three functional groups. Specifically, we manipulated the amount of variation in environmental tolerance and in maximum growth rate, and explored how trait variation influenced anoxic-oxic regime shifts along a gradient of oxygen influx. We found that greater diversity of either cyanobacteria or sulfate-reducing bacteria increased the resilience of the ecosystem state that these groups dominated, while greater diversity of phototrophic sulfur bacteria reduced the resilience of the state they dominated. We also found that simultaneous variation in multiple functional groups reduced, reversed, or did not change the diversity effect of individual functional groups. Collectively, our findings highlight the importance of considering multiple interacting functional groups when predicting the effect of functional diversity on ecosystem resilience

@@

{>> Add a more detailed description of the model and the additions <<}
{>>TODO<<}

@@

1. Standard R help for each function (`?COMMAND` in R)
2. Two vignettes acompanying the package:
  - A **User Guide**, also available on the R-Universe [Vignette 1](@LINK_NEEDED). This gives an introduction of the package and its functions and provides a walk-through of the process of running, visualizing and extra
   and [Vignette 2](@LINK_NEEDED)
3. This paper as a third vignette, also available under RUniverse [Vignette 3](@LINK_NEEDED)

@@

{>>More details from the paper.<<}
{>>Romana will provide two or three sentences<<}
